### 2019-02-20 sections/intuition.tex
intuition collaboration: remove editors
Fix in wording

The central objective of \TOP is to \emph{coordinate collaboration}.
The basic building blocks of \TOPHAT for this are task combinators.
They express ways in which people can work together.
Tasks can be executed after each other, at the same time, or conditionally.
This motivates the combinators step ($\Then$, $\Next$), parallel ($\And$), and choice ($\Or$, $\Xor$).

@@

The step combinators give rise to a form of internal communication:
They represent data flow that \emph{follows} control flow.

>>>>

The central objective of \TOP is to \emph{coordinate collaboration}.
The basic building blocks of \TOPHAT for expressing collaboration are task combinators.
They express ways in which people can work together.
Tasks can be executed after each other, at the same time, or conditionally.
This motivates the combinators step, parallel, and choice.

@@

The step combinators give rise to a form of internal communication:
They represent data flow that \emph{follows} control flow.
\fixme{example with paper deadline}
